MSAD_PCA_Walkthrough

### 2017-07-13 LaTeX_Vignette/MS-MVSPC_DissertationVignette.tex
Finished draft 2 edits.

This section provides a fully commented code walk-through for the main \texttt{msp*} functions in the \texttt{mvMonitoring} package. This package depends on a few other packages, but most of these dependencies are on commonly-used packages. The exception is \texttt{BMS}.
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlkwd{library}\hlstd{(devtools)}
\hlkwd{library}\hlstd{(xts)}
\hlcom{# install.packages("BMS") # If necessary}
\hlkwd{build}\hlstd{(}\hlstr{"C:/Users/gabriel_odom/Documents/GitHub/mvMonitoring/mvMonitoring"}\hlstd{)}
\end{alltt}
\begin{verbatim}
## [1] "C:/Users/gabriel_odom/Documents/GitHub/mvMonitoring/mvMonitoring_0.1.1.tar.gz"
\end{verbatim}
\begin{alltt}
\hlkwd{library}\hlstd{(mvMonitoring)}
\end{alltt}
\end{kframe}
\end{knitrout}

\subsection{Generating Synthetic Data}
First begin by generating multi-state data from a fault scenario. This code will yield observations under Fault 2A, as described the Synthetic Fault Induction section. We choose the default options for the period length (7 days * 24 hours * 60 minutes = 10,080 observations), the starting index of the fault (8500 out of 10080), and the time stamp for beginning the data is 16 May of 2016 at 10:00AM (my wedding anniversary). As we can see from the \texttt{str()} function, we have an \texttt{xts} matrix with 10080 rows and four columns (the state indicator and the three features).

@@

\subsection{Train the Fault Detection Threshold}
Now that these observations are generated and stored in memory, the \texttt{mspTrain} function can train the MSAD-PCA model. The last 1620 observations (27 hours' worth) will be saved for testing. The \texttt{mspTrain} function takes in the training data set partitioned between the observation and the label column. If this function errors, make sure the label column is not included in the data matrix -- this will cause a singularity in the data. The function will
\begin{enumerate}
\item Train on the first three days' worth of observations, as set by \texttt{trainObs}.
%
\item Scan the fourth day for anomalies, as set by \texttt{updateFreq}.
%
\item Remove any alarmed observations.
%
\item ``Forget'' the first day's observations.
%
\item ``Learn'' the non-alarmed observations from the fourth day.
%
\item Retrain and repeat until the end of the data matrix
\end{enumerate}

@@

##   Data: num [1:4142, 1:5] 0.28 0.201 1.208 0.919 0.418 ...

@@

##   .. ..$ SPE_threshold   : Named num 4.29

@@

##   .. ..$ T2_threshold    : Named num 62.6

@@

##   .. ..$ projectionMatrix: num [1:6, 1:2] 0.422 -0.386 0.435 0.431 -0.318 ...
##   .. ..$ LambdaInv       : num [1:2, 1:2] 0.204 0 0 1.606
##   .. ..$ muTrain         : Named num [1:6] 1.37 -2.1 2.95 1.36 -2.06 ...

@@

##   .. ..$ RootPrecisTrain : num [1:6, 1:6] 2.64 0 0 0 0 ...

@@

##   .. ..$ SPE_threshold   : Named num 1.16

@@

##   .. ..$ T2_threshold    : Named num 74.2

@@

##   .. ..$ projectionMatrix: num [1:6, 1:3] -0.4957 -0.0668 0.4887 -0.5236 -0.1866 ...
##   .. ..$ LambdaInv       : num [1:3, 1:3] 0.284 0 0 0 0.712 ...
##   .. ..$ muTrain         : Named num [1:6] 2.978 -0.566 -4.508 2.95 -0.592 ...

@@

##   .. ..$ RootPrecisTrain : num [1:6, 1:6] 1.08 0 0 0 0 ...

@@

##   .. ..$ SPE_threshold   : Named num 8.04

@@

##   .. ..$ T2_threshold    : Named num 80.8

@@

##   .. ..$ projectionMatrix: num [1:6, 1:2] -0.392 -0.452 -0.454 0.163 -0.462 ...
##   .. ..$ LambdaInv       : num [1:2, 1:2] 0.278 0 0 0.493
##   .. ..$ muTrain         : Named num [1:6] 0.528 0.268 1.413 0.57 0.254 ...

@@

##   .. ..$ RootPrecisTrain : num [1:6, 1:6] 17.4 0 0 0 0 ...

@@

\item \texttt{FaultChecks}: An \texttt{xts} matrix of monitoring statistics and associated indicators for all observations after the burn-in of \texttt{trainObs}. It will have 10080 - \texttt{trainObs} number of rows and five columns:

@@

\item \texttt{Non\_Alarmed\_Obs}: An \texttt{xts} matrix will all observations with an alarm code of 0 from \texttt{FaultChecks}. Of note, this matrix contains the data, while the \texttt{FaultChecks} matrix only contains the monitoring statistics and indicators.

@@

\subsubsection{Adding Lagged Features}
First, concatenate the last given observation from the training set as ``row 0'' of the test data set. This will enable \texttt{mspMonitor} to include lag-1 features. Similarly, one would include the last $k$ observations of the training set should the process dictate the need for any lag-$k$ features. Because the Fault Start Index was set to 8500, this testing window will show the change point between observations generated under normal conditions and those generated under a fault state.
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{test1A_xts} \hlkwb{<-} \hlstd{fault1A_xts[}\hlnum{8460}\hlopt{:}\hlnum{8520}\hlstd{,} \hlopt{-}\hlnum{1}\hlstd{]}
\hlstd{lagTest1A_xts} \hlkwb{<-} \hlkwd{lag.xts}\hlstd{(test1A_xts,} \hlnum{0}\hlopt{:}\hlnum{1}\hlstd{)}
\hlstd{lagTest1A_xts} \hlkwb{<-} \hlkwd{cbind}\hlstd{(fault1A_xts[}\hlnum{8461}\hlopt{:}\hlnum{8520}\hlstd{,}\hlnum{1}\hlstd{],}
                       \hlstd{lagTest1A_xts[}\hlopt{-}\hlnum{1}\hlstd{,])}
\hlkwd{head}\hlstd{(lagTest1A_xts)}
\end{alltt}
\begin{verbatim}
##                     state         x         y         z       x.1
## 2015-05-22 07:00:00     1 0.5454353 -1.494528 0.9296569 0.4159290
## 2015-05-22 07:01:00     1 0.5752773 -1.638525 1.1806822 0.5454353
## 2015-05-22 07:02:00     1 0.5381703 -1.448424 1.0029127 0.5752773
## 2015-05-22 07:03:00     1 0.6097887 -1.320156 0.9345597 0.5381703
## 2015-05-22 07:04:00     1 0.8534018 -1.555631 1.0922745 0.6097887
## 2015-05-22 07:05:00     1 0.7252695 -1.792569 1.1605990 0.8534018
##                            y.1       z.1
## 2015-05-22 07:00:00  0.1063122 0.3767823
## 2015-05-22 07:01:00 -1.4945284 0.9296569
## 2015-05-22 07:02:00 -1.6385255 1.1806822
## 2015-05-22 07:03:00 -1.4484243 1.0029127
## 2015-05-22 07:04:00 -1.3201558 0.9345597
## 2015-05-22 07:05:00 -1.5556311 1.0922745
\end{verbatim}
\end{kframe}
\end{knitrout}

\subsubsection{Monitoring the Test Data}
With the lagged test observations in the working environment, the \texttt{mspMonitor} function can be applied. This function (similarly to \texttt{mspTrain}) takes in the label information as a separate argument from the input data. Further, the \texttt{mspMonitor} function takes in the \texttt{TrainingSpecs} object returned in the results list from \texttt{mspTrain}. Notice that the first six rows of the monitor matrix are the exact same as the first six rows of the lagged test matrix, except that the rows of the monitor matrix have the monitoring statistic and corresponding indicator columns appended.
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{monitor1A_xts} \hlkwb{<-} \hlkwd{mspMonitor}\hlstd{(}\hlkwc{observations} \hlstd{= lagTest1A_xts[,}\hlopt{-}\hlnum{1}\hlstd{],}
                            \hlkwc{labelVector} \hlstd{= lagTest1A_xts[,}\hlnum{1}\hlstd{],}
                            \hlkwc{trainingSummary} \hlstd{= train1A_ls}\hlopt{$}\hlstd{TrainingSpecs)}
\hlkwd{head}\hlstd{(monitor1A_xts)}
\end{alltt}
\begin{verbatim}
##                             x         y         z       x.1        y.1
## 2015-05-22 07:00:00 0.5454353 -1.494528 0.9296569 0.4159290  0.1063122
## 2015-05-22 07:01:00 0.5752773 -1.638525 1.1806822 0.5454353 -1.4945284
## 2015-05-22 07:02:00 0.5381703 -1.448424 1.0029127 0.5752773 -1.6385255
## 2015-05-22 07:03:00 0.6097887 -1.320156 0.9345597 0.5381703 -1.4484243
## 2015-05-22 07:04:00 0.8534018 -1.555631 1.0922745 0.6097887 -1.3201558
## 2015-05-22 07:05:00 0.7252695 -1.792569 1.1605990 0.8534018 -1.5556311
##                           z.1       SPE SPE_Flag        T2 T2_Flag Alarm
## 2015-05-22 07:00:00 0.3767823 0.8309122        0 27.233955       0    NA
## 2015-05-22 07:01:00 0.9296569 0.0575549        0  4.361359       0    NA
## 2015-05-22 07:02:00 1.1806822 0.4782941        0  5.062568       0    NA
## 2015-05-22 07:03:00 1.0029127 1.0857386        0  5.471633       0    NA
## 2015-05-22 07:04:00 0.9345597 0.2959896        0  4.626291       0    NA
## 2015-05-22 07:05:00 1.0922745 0.3100297        0  2.913877       0    NA
\end{verbatim}
\end{kframe}
\end{knitrout}

\subsection{Warn Operators During Alarms}
Note that all `Alarm` codes in the monitor matrix above are recorded with \texttt{NA} values. This is because the \texttt{mspMonitor} function does not check the sequential flag conditions of the monitor matrix. This is the responsibility of the \texttt{mspWarning} function. Because the \texttt{mspWarning} function is designed to test one incoming observation at a time through a script or batch file, the following example is designed to mimic the behavior of the \texttt{mspWarning} function as each new observation comes online.
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{alarm1A_xts} \hlkwb{<-} \hlstd{monitor1A_xts}
\hlkwa{for}\hlstd{(i} \hlkwa{in} \hlnum{1}\hlopt{:}\hlkwd{nrow}\hlstd{(alarm1A_xts))\{}
  \hlkwa{if}\hlstd{(i} \hlopt{<} \hlstd{(}\hlnum{5} \hlopt{+} \hlnum{1}\hlstd{))\{}
    \hlstd{alarm1A_xts[}\hlnum{1}\hlopt{:}\hlstd{i,]} \hlkwb{<-} \hlkwd{mspWarning}\hlstd{(alarm1A_xts[}\hlnum{1}\hlopt{:}\hlstd{i,])}
  \hlstd{\}}\hlkwa{else}\hlstd{\{}
    \hlstd{alarm1A_xts[(i} \hlopt{-} \hlnum{5}\hlstd{)}\hlopt{:}\hlstd{i,]} \hlkwb{<-} \hlkwd{mspWarning}\hlstd{(alarm1A_xts[(i} \hlopt{-} \hlnum{5}\hlstd{)}\hlopt{:}\hlstd{i,])}
  \hlstd{\}}
\hlstd{\}}
\end{alltt}
\end{kframe}
\end{knitrout}
The fault was introduced at index 8500, which corresponds to about 40 minutes into the test hour.
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlkwd{plot}\hlstd{(alarm1A_xts[,} \hlkwd{ncol}\hlstd{(alarm1A_xts)],}
     \hlkwc{main} \hlstd{=} \hlstr{"Alarm Codes for Test Data"}\hlstd{)}
\end{alltt}
\end{kframe}
\includegraphics[width=\maxwidth]{figure/r_warning_Plot-1}

\end{knitrout}
The alarm codes are
\begin{enumerate}
\item ``0'': No alarm.
\item ``1'': Hotelling's $T^2$ alarm.
\item ``2'': Squared Prediction Error alarm.
\item ``3'': Both alarms.
\end{enumerate}
As we can see, the monitoring function detects a process anomaly after 40 minutes into the test hour, and the warning function issues the corresponding alarms.

@@

\section{Conclusion} \label{sec:D_Conclusion}
We have supplied our motivation for this package, and we have discussed implementing a multivariate process monitoring scheme with this package using the example of a decentralized WWT plant in Golden, CO. We believe that this software will provide system engineers with the tools necessary to quickly and accurately detect abnormalities in multivariate, autocorrelated, non-stationary, non-linear, and multi-state water treatment systems. Further, we have given a synthetic example showing how the functions within this package would be implemented and tuned in practice.

>>>>

This section provides a fully commented code walk-through for the main \texttt{msp.*} functions in the \texttt{mvMonitoring} package. This package depends on few other packages, and most of these dependencies are on commonly-used packages. The exception is \texttt{BMS}.
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlkwd{library}\hlstd{(devtools)}
\hlkwd{library}\hlstd{(xts)}
\hlcom{# install.packages("BMS") # If necessary}
\hlkwd{build}\hlstd{(}\hlstr{"C:/Users/gabriel_odom/Documents/GitHub/mvMonitoring/mvMonitoring"}\hlstd{)}
\end{alltt}
\begin{verbatim}
## [1] "C:/Users/gabriel_odom/Documents/GitHub/mvMonitoring/mvMonitoring_0.1.1.tar.gz"
\end{verbatim}
\begin{alltt}
\hlkwd{library}\hlstd{(mvMonitoring)}
\end{alltt}
\end{kframe}
\end{knitrout}

\subsection{Generating Synthetic Data}
First, begin by generating multi-state data from a fault scenario. This code will yield observations under Fault 2A, as described in Section \ref{subsec:D_FaultDefns}. We choose the default options for the period length (7 days * 24 hours * 60 minutes = 10,080 observations), the starting index of the fault (8500 out of 10080), and the time stamp for beginning the data is 16 May of 2016 at 10:00AM (my wedding anniversary). As we can see from the structure of the output, \texttt{mspProcessData} returns an \texttt{xts} matrix with 10080 rows and four columns (the state indicator and the three features).

@@

\subsection{Train the Fault Detection Threshold}
Now that these observations are generated and stored in memory, the \texttt{mspTrain} function can train the MSAD-PCA model. The last 1620 observations (27 hours' worth) will be saved for validation. The \texttt{mspTrain} function takes in the training data matrix and corresponding class label column. If this function errors, make sure the label column is not included in the data matrix -- the constant values will cause a rank deficiency training covariance matrix. The \texttt{mspTrain} function will
\begin{enumerate}
\item Train on the first three days' worth of observations, as set by \texttt{trainObs}.
%
\item Scan the fourth day for anomalies, as set by \texttt{updateFreq}.
%
\item Remove any alarmed observations.
%
\item ``Forget'' the first day's observations.
%
\item ``Learn'' the non-alarmed observations from the fourth day.
%
\item Retrain and repeat until the end of the training matrix.
\end{enumerate}

@@

##   Data: num [1:4142, 1:5] 1.205 0.195 1.304 1.5 1.458 ...

@@

##   .. ..$ SPE_threshold   : Named num 5.59

@@

##   .. ..$ T2_threshold    : Named num 59.1

@@

##   .. ..$ projectionMatrix: num [1:6, 1:2] 0.426 -0.378 0.439 0.435 -0.303 ...
##   .. ..$ LambdaInv       : num [1:2, 1:2] 0.209 0 0 1.458
##   .. ..$ muTrain         : Named num [1:6] 1.39 -2.1 2.99 1.37 -2.06 ...

@@

##   .. ..$ RootPrecisTrain : num [1:6, 1:6] 2.67 0 0 0 0 ...

@@

##   .. ..$ SPE_threshold   : Named num 0.851

@@

##   .. ..$ T2_threshold    : Named num 74.8

@@

##   .. ..$ projectionMatrix: num [1:6, 1:3] -0.494 -0.0815 0.4886 -0.522 -0.195 ...
##   .. ..$ LambdaInv       : num [1:3, 1:3] 0.283 0 0 0 0.732 ...
##   .. ..$ muTrain         : Named num [1:6] 2.981 -0.57 -4.51 2.954 -0.597 ...

@@

##   .. ..$ RootPrecisTrain : num [1:6, 1:6] 1.1 0 0 0 0 ...

@@

##   .. ..$ SPE_threshold   : Named num 5.49

@@

##   .. ..$ T2_threshold    : Named num 82.5

@@

##   .. ..$ projectionMatrix: num [1:6, 1:2] 0.393 0.445 0.448 -0.18 0.466 ...
##   .. ..$ LambdaInv       : num [1:2, 1:2] 0.278 0 0 0.496
##   .. ..$ muTrain         : Named num [1:6] 0.531 0.272 1.437 0.573 0.258 ...

@@

##   .. ..$ RootPrecisTrain : num [1:6, 1:6] 18.4 0 0 0 0 ...

@@

\item \texttt{FaultChecks}: An \texttt{xts} matrix of monitoring statistics and associated indicators for all observations after the burn-in of \texttt{trainObs}. It will have 8461 - \texttt{trainObs} number of rows and five columns:

@@

\item \texttt{Non\_Alarmed\_Obs}: An \texttt{xts} matrix containing all observations with an alarm code of 0 from \texttt{FaultChecks}. Of note, this matrix contains the data, while the \texttt{FaultChecks} matrix only contains the monitoring statistics and indicators.

@@

\subsubsection{Adding Lagged Features}
First, concatenate the last given observation from the training set as ``row 0'' of the test data set. This will enable \texttt{mspMonitor} to include lag-1 features. Similarly, one would include the last $k$ observations of the training set should the process dictate the need for any lag-$k$ features. Because the Fault Start Index was set to 8500, this testing window will show the change point between observations generated under normal conditions and those generated under a fault state.
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{test1A_xts} \hlkwb{<-} \hlstd{fault1A_xts[}\hlnum{8460}\hlopt{:}\hlnum{8520}\hlstd{,} \hlopt{-}\hlnum{1}\hlstd{]}
\hlstd{lagTest1A_xts} \hlkwb{<-} \hlkwd{lag.xts}\hlstd{(test1A_xts,} \hlnum{0}\hlopt{:}\hlnum{1}\hlstd{)}
\hlstd{lagTest1A_xts} \hlkwb{<-} \hlkwd{cbind}\hlstd{(fault1A_xts[}\hlnum{8461}\hlopt{:}\hlnum{8520}\hlstd{,}\hlnum{1}\hlstd{],}
                       \hlstd{lagTest1A_xts[}\hlopt{-}\hlnum{1}\hlstd{,])}
\hlkwd{head}\hlstd{(lagTest1A_xts)}
\end{alltt}
\begin{verbatim}
##                     state         x         y         z       x.1
## 2015-05-22 07:00:00     1 0.4945284 -1.376417 0.7072224 0.3745871
## 2015-05-22 07:01:00     1 0.6357969 -1.547100 0.9991109 0.4945284
## 2015-05-22 07:02:00     1 0.6318896 -1.535374 1.0846997 0.6357969
## 2015-05-22 07:03:00     1 0.6712189 -1.521690 0.8632718 0.6318896
## 2015-05-22 07:04:00     1 0.6971078 -1.665835 0.8971302 0.6712189
## 2015-05-22 07:05:00     1 0.9239645 -1.632949 1.0113845 0.6971078
##                             y.1       z.1
## 2015-05-22 07:00:00  0.08531597 0.3699029
## 2015-05-22 07:01:00 -1.37641739 0.7072224
## 2015-05-22 07:02:00 -1.54709995 0.9991109
## 2015-05-22 07:03:00 -1.53537382 1.0846997
## 2015-05-22 07:04:00 -1.52168971 0.8632718
## 2015-05-22 07:05:00 -1.66583498 0.8971302
\end{verbatim}
\end{kframe}
\end{knitrout}

\subsubsection{Monitoring the Test Data}
With the lagged test observations in the working environment, the \texttt{mspMonitor} function can be applied. This function (similarly to \texttt{mspTrain}) takes in the label information as a separate argument from the input data. Further, the \texttt{mspMonitor} function takes in the \texttt{TrainingSpecs} object returned in the results list from \texttt{mspTrain}. Notice that the first six rows of the matrix returned by \texttt{mspMonitor} are the exact same as the first six rows of the lagged test matrix, except that the rows of the matrix from the \texttt{mspMonitor} function have the monitoring statistics and corresponding indicator columns appended.
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{monitor1A_xts} \hlkwb{<-} \hlkwd{mspMonitor}\hlstd{(}\hlkwc{observations} \hlstd{= lagTest1A_xts[,}\hlopt{-}\hlnum{1}\hlstd{],}
                            \hlkwc{labelVector} \hlstd{= lagTest1A_xts[,}\hlnum{1}\hlstd{],}
                            \hlkwc{trainingSummary} \hlstd{= train1A_ls}\hlopt{$}\hlstd{TrainingSpecs)}
\hlkwd{head}\hlstd{(monitor1A_xts)}
\end{alltt}
\begin{verbatim}
##                             x         y         z       x.1         y.1
## 2015-05-22 07:00:00 0.4945284 -1.376417 0.7072224 0.3745871  0.08531597
## 2015-05-22 07:01:00 0.6357969 -1.547100 0.9991109 0.4945284 -1.37641739
## 2015-05-22 07:02:00 0.6318896 -1.535374 1.0846997 0.6357969 -1.54709995
## 2015-05-22 07:03:00 0.6712189 -1.521690 0.8632718 0.6318896 -1.53537382
## 2015-05-22 07:04:00 0.6971078 -1.665835 0.8971302 0.6712189 -1.52168971
## 2015-05-22 07:05:00 0.9239645 -1.632949 1.0113845 0.6971078 -1.66583498
##                           z.1       SPE SPE_Flag        T2 T2_Flag Alarm
## 2015-05-22 07:00:00 0.3699029 1.2098887        0 27.458819       0    NA
## 2015-05-22 07:01:00 0.7072224 0.1235024        0  5.798909       0    NA
## 2015-05-22 07:02:00 0.9991109 0.3013605        0  4.793520       0    NA
## 2015-05-22 07:03:00 1.0846997 0.4092379        0  4.901590       0    NA
## 2015-05-22 07:04:00 0.8632718 0.1091666        0  4.492368       0    NA
## 2015-05-22 07:05:00 0.8971302 0.6033914        0  3.749758       0    NA
\end{verbatim}
\end{kframe}
\end{knitrout}

\subsection{Warn Operators During Alarms}
Note that all values in the \texttt{Alarm} column of the returned matrix above are recorded with \texttt{NA} values. This is because the \texttt{mspMonitor} function does not check the monitor output matrix for the sequential flags necessary to trigger an alarm. This is the responsibility of the \texttt{mspWarning} function. Because the \texttt{mspWarning} function is designed to test one incoming observation at a time through a script or batch file, the following example is designed to mimic the behavior of the \texttt{mspWarning} function as each new observation comes online.
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{alarm1A_xts} \hlkwb{<-} \hlstd{monitor1A_xts}
\hlkwa{for}\hlstd{(i} \hlkwa{in} \hlnum{1}\hlopt{:}\hlkwd{nrow}\hlstd{(alarm1A_xts))\{}
  \hlkwa{if}\hlstd{(i} \hlopt{<} \hlstd{(}\hlnum{5} \hlopt{+} \hlnum{1}\hlstd{))\{}
    \hlstd{alarm1A_xts[}\hlnum{1}\hlopt{:}\hlstd{i,]} \hlkwb{<-} \hlkwd{mspWarning}\hlstd{(alarm1A_xts[}\hlnum{1}\hlopt{:}\hlstd{i,])}
  \hlstd{\}}\hlkwa{else}\hlstd{\{}
    \hlstd{alarm1A_xts[(i} \hlopt{-} \hlnum{5}\hlstd{)}\hlopt{:}\hlstd{i,]} \hlkwb{<-} \hlkwd{mspWarning}\hlstd{(alarm1A_xts[(i} \hlopt{-} \hlnum{5}\hlstd{)}\hlopt{:}\hlstd{i,])}
  \hlstd{\}}
\hlstd{\}}
\end{alltt}
\end{kframe}
\end{knitrout}
\noindent The fault was introduced at index 8500, which corresponds to about 40 minutes into the test hour.
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlkwd{plot}\hlstd{(alarm1A_xts[,} \hlkwd{ncol}\hlstd{(alarm1A_xts)],}
     \hlkwc{main} \hlstd{=} \hlstr{"Alarm Codes for Test Data"}\hlstd{)}
\end{alltt}
\end{kframe}
\includegraphics[width=\maxwidth]{figure/r_warning_Plot-1}

\end{knitrout}
\noindent The alarm codes are
\begin{enumerate}
\item ``0'': No alarm.
\item ``1'': Hotelling's $T^2$ alarm.
\item ``2'': Squared Prediction Error alarm.
\item ``3'': Both alarms.
\end{enumerate}
\noindent As we can see, the monitoring function detects a process anomaly after 40 minutes into the test hour, and the warning function issues the corresponding alarms.

@@

\section{Conclusion} \label{sec:D_Conclusion}
We have supplied our motivation for this package, and we have discussed implementing a multivariate process monitoring scheme with this package using synthetic data. We believe that this software will provide system engineers with the tools necessary to quickly and accurately detect abnormalities in multivariate, autocorrelated, non-stationary, non-linear, and multi-state industrial and engineering systems. Further, we have given a synthetic example showing how the functions within this package would be implemented and tuned in practice.
